Verifying Demonstrations

### 2018-02-19 paper/ZKPK.tex
Adds Schnorr algorithm as instantiation of SPK

\paragraph{Implementations}

There are various implementations.
We will rely on the Schnorr identification scheme~\cite{Schnorr}.

@@

The notation in \cref{PKexample} could equivalently be seen as
\begin{equation*}
  \PKprove[g,h,y,y',q,\alpha,\beta,\gamma] \leftrightarrow
  \PKverify[g,h,y,y',q],
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (1) or reject (0).

>>>>

\subsection{Instantiations}

@@

We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
    \prod_{i=1}^n g_i^{\alpha_i}}\).
This could equivalently be written as
\begin{equation*}
  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
  \PKverify[\{g_i\}_i, q, A],
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (1) or reject (0).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\PKprove[g, q, A, \alpha]\):
    &
    & \(\PKverify[g, q, A]\):
    \\

  \end{tabular}
  \caption{%
    \(\PK{\alpha}{A = g^\alpha}\) using the Schnorr identification scheme.
  }%
  \label{PKalgorithms}
\end{figure*}

\NewAlgorithm{\SPKprove}{SPK.\!Prove}
\NewAlgorithm{\SPKverify}{SPK.\!Verify}

For the non-interactive instance, \(\SPK{\alpha}{A = g^\alpha}{m}\), we use the 
Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.

\begin{figure*}
  \begin{minipage}[t]{0.48\linewidth}
    \begin{algorithmic}
      \Function{$\SPKprove$}{$g, q, A, \alpha, m$}
        \State{$\rho\rgets \Z_q, R\gets g^\rho$}
        \State{$c \gets H(g|A|R|m)$}
        \State{$s \gets \rho - c\alpha$}
        \State{\Return{$(s, c)$}}
      \EndFunction{}
    \end{algorithmic}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\linewidth}
    \begin{algorithmic}
      \Function{$\SPKverify$}{$g, q, A, m, s, c$}
        \State{$\hat R \gets g^s A^c$}
        \If{$c = H(g|A|\hat R|m)$}
          \State{\Return{1}}
        \Else{}
          \State{\Return{0}}
        \EndIf{}
      \EndFunction{}
    \end{algorithmic}
  \end{minipage}
  \caption{%
    \(\SPK{\alpha}{A = g^\alpha}{m}\) using the Fiat-Shamir heuristic on the 
    Schnorr identification scheme.
  }%
  \label{SPKalgorithms}
\end{figure*}
